\label{acknowledgement}
\paragraph{}
I would like to thank many people for their help over the years in teaching me about the HPX system, C++, software development, many other aspects of producing quality research, as well as how to be a good human. First of all I am indebted to my parents for inculcating in me an appreciation for learning, hard work, and beauty in the arts. I also would like to thank the many teachers, like Mrs. Breaux, Mrs. Jones, and Ms. Cain, who, when I was younger, took an interest in my future, even when I lacked vision for what that future could be. I would like to thank Dr. Dennis Castleberry for igniting my interest in software, and opening a door into a fascinating world full of difficult problems which provides not only the opportunity for satisfying work, but the opportunity to benefit others by its fruit. I would like to also thank Dr. Samuel Kellar, Dr. Bibek Wagle, and Adrian Lemoine for teaching me about HPX and C++ which, while never formally being their responsibility, they were always more than happy to do. Last, but certainly not least, I would like to thank Dr. Hartmut Kaiser, my mentor and friend, for taking an interest in my development as a software developer and researcher, and who was willing to give me a chance to continue my studies in the Master's program knowing that I would benefit from my involvement at CCT and the Ste||ar Group far more than he, or the Ste||ar Group, ever would.

%Make sure there is one blank line at the end of the Acknowledgments text.
